---
format: html
html-table-processing: none
---
```{r}
library(gt)
library(tidyverse)
```

# GTSQL Examples Corpus

Paired **gt** (R) and **GTSQL** examples reproducing the same display table.
Examples are drawn from [*Creating Effective Display Tables with the gt
Package*](https://rich-iannone.github.io/gt-effective-display-tables/) and the
[gt reference](https://gt.rstudio.com/reference/).

Only examples reproducible with the clauses defined in
[GTSQL_PLAN.md](GTSQL_PLAN.md) are included. Excluded gt features (no GTSQL
equivalent today) include: `tab_row_group()` explicit row groups (basic
`groupname_col` grouping *is* supported via `FACET <column>`), multi-column
stubs, `tab_stub_indent()`, `tab_footnote()`, per-cell footnotes, `row_order()`,
`tab_spanner_delim()`, `cols_add()`, `grand_summary_rows()`, `text_transform()`
with arbitrary R functions, `from_column()` dynamic parameters, nanoplots, and
`tab_options()` theme tuning.

Each example assumes a SQL data source whose schema matches the corresponding R
dataset (e.g. a `gtcars` table mirroring the `gtcars` tibble).

---

## 1. Minimal table — all columns

**gt**
```{r}
exibble |>
  gt()
```

**GTSQL**
```sql
SELECT * FROM exibble
TABULATE
```

---

## 2. Column selection and reordering

**gt**
```{r}
gtcars |>
  dplyr::select(mfr, model, year, hp) |>
  dplyr::slice_head(n = 6) |>
  gt()
```

**GTSQL**
```sql
SELECT mfr, model, year, hp FROM gtcars LIMIT 6
TABULATE
```

---

## 3. Stub from a row-label column

**gt**
```{r}
gtcars |>
  dplyr::select(model, year, hp, trq) |>
  dplyr::slice(1:5) |>
  gt(rowname_col = "model") |>
  tab_stubhead(label = "car")
```

**GTSQL**
```sql
SELECT model, year, hp, trq FROM gtcars LIMIT 5
TABULATE
FORMAT STUB model AS model_head
LABEL model_head => 'car'
```

---

## 4. Header with title and subtitle

**gt**
```{r}
gtcars |>
  dplyr::select(mfr, model, msrp) |>
  dplyr::slice(1:5) |>
  gt() |>
  tab_header(
    title = "Data listing from gtcars",
    subtitle = "gtcars is an R dataset"
  )
```

**GTSQL**
```sql
SELECT mfr, model, msrp FROM gtcars LIMIT 5
TABULATE
LABEL
  title => 'Data listing from gtcars',
  subtitle => 'gtcars is an R dataset'
```

---

## 5. Header + source-note caption + column labels

**gt**
```{r}
towny |>
  dplyr::select(name, population_2021, density_2021) |>
  dplyr::slice_max(population_2021, n = 8) |>
  gt() |>
  tab_header(
    title = "Ontario's Largest Municipalities",
    subtitle = "Population and density from the 2021 census"
  ) |>
  fmt_integer(columns = c(population_2021, density_2021)) |>
  cols_label(
    name = "Municipality",
    population_2021 = "Population",
    density_2021 = "Density (per km²)"
  ) |>
  tab_source_note(source_note = "Source: Statistics Canada")
```

**GTSQL**
```sql
SELECT name, population_2021, density_2021
FROM towny
ORDER BY population_2021 DESC
LIMIT 8

TABULATE
FORMAT population_2021, density_2021
  RENAMING * => '{:num %\'d}'
LABEL
  title => 'Ontario''s Largest Municipalities',
  subtitle => 'Population and density from the 2021 census',
  caption => 'Source: Statistics Canada',
  name => 'Municipality',
  population_2021 => 'Population',
  density_2021 => 'Density (per km²)'
```

---

## 6. Single spanner over related columns

**gt**
```{r}
gtcars |>
  dplyr::select(year, model, bdy_style, starts_with(c("hp", "trq", "mpg"))) |>
  dplyr::slice(1:8) |>
  gt(rowname_col = "model") |>
  tab_spanner(
    label = "performance",
    columns = starts_with(c("hp", "trq", "mpg"))
  )
```

**GTSQL**
```sql
SELECT year, model, bdy_style, hp, hp_rpm, trq, trq_rpm, mpg_c, mpg_h
FROM gtcars LIMIT 8

TABULATE
FORMAT STUB model
FORMAT SPAN hp, hp_rpm, trq, trq_rpm, mpg_c, mpg_h AS performance
```

---

## 7. Two side-by-side spanners

**gt**
```{r}
towny |>
  dplyr::arrange(desc(population_2021)) |>
  dplyr::slice_head(n = 5) |>
  dplyr::select(name, ends_with("2016"), ends_with("2021")) |>
  gt() |>
  tab_spanner(columns = starts_with("pop"),     label = "Population") |>
  tab_spanner(columns = starts_with("den"),     label = "Density")
```

**GTSQL**
```sql
SELECT name, population_2016, density_2016, population_2021, density_2021
FROM towny
ORDER BY population_2021 DESC
LIMIT 5

TABULATE name, population_2016, population_2021, density_2016, density_2021
FORMAT SPAN population_2016, population_2021 AS population
FORMAT SPAN density_2016, density_2021 AS density
LABEL
  population => 'Population',
  density => 'Density'
```

---

## 8. Nested (stacked) spanners

**gt**
```{r}
towny |>
  dplyr::arrange(desc(population_2021)) |>
  dplyr::slice_head(n = 5) |>
  dplyr::select(name, ends_with("2016"), ends_with("2021")) |>
  gt() |>
  tab_spanner(columns = c(population_2016, population_2021), label = "Population", id = "pop") |>
  tab_spanner(columns = c(density_2016, density_2021),       label = "Density",    id = "den") |>
  tab_spanner(spanners = c("pop", "den"), label = "2016–2021 Comparison")
```

**GTSQL**
```sql
SELECT name, population_2016, population_2021, density_2016, density_2021
FROM towny
ORDER BY population_2021 DESC
LIMIT 5

TABULATE name, population_2016, population_2021, density_2016, density_2021
FORMAT SPAN population_2016, population_2021 AS population
FORMAT SPAN density_2016, density_2021 AS density
FORMAT SPAN population, density AS comparison
LABEL
  population => 'Population',
  density => 'Density',
  comparison => '2016–2021 Comparison'
```

---

## 9. Hide a column

**gt**
```{r}
gtcars |>
  dplyr::select(mfr, model, year, hp) |>
  dplyr::slice_head(n = 6) |>
  gt() |>
  cols_hide(columns = mfr)
```

**GTSQL**
```sql
SELECT mfr, model, year, hp FROM gtcars LIMIT 6
TABULATE
FORMAT mfr
  SETTING hide => true
```

---

## 10. Column widths and alignment

**gt**
```{r}
gtcars |>
  dplyr::select(model, hp, msrp) |>
  dplyr::slice(1:5) |>
  gt() |>
  cols_align(align = "right",  columns = c(hp, msrp)) |>
  cols_width(
    model ~ px(180),
    hp    ~ px(80),
    msrp  ~ px(120)
  )
```

**GTSQL**
```sql
SELECT model, hp, msrp FROM gtcars LIMIT 5
TABULATE
FORMAT model
  SETTING width => '180px'
FORMAT hp
  SETTING width => '80px', align => 'right'
FORMAT msrp
  SETTING width => '120px', align => 'right'
```

---

## 11. Number formatting — 3 decimals, no separators

**gt**
```{r}
exibble |>
  dplyr::select(num, char) |>
  gt() |>
  fmt_number(columns = num, decimals = 3, use_seps = FALSE)
```

**GTSQL**
```sql
TABULATE num, char FROM exibble
FORMAT num
  RENAMING * => '{:num %.3f}'
```

---

## 12. Integer formatting with digit separators

**gt**
```{r}
exibble |>
  dplyr::select(num, char) |>
  gt() |>
  fmt_integer(columns = num)
```

**GTSQL**
```sql
TABULATE num, char FROM exibble
FORMAT num
  RENAMING * => '{:num %\'d}'
```

---

## 13. Currency formatting (USD)

**gt**
```{r}
gtcars |>
  dplyr::select(model, year, hp, msrp) |>
  dplyr::slice_head(n = 8) |>
  gt(rowname_col = "model") |>
  fmt_integer(columns = hp) |>
  fmt_currency(columns = msrp, currency = "USD", decimals = 0)
```

**GTSQL**
```sql
SELECT model, year, hp, msrp FROM gtcars LIMIT 8
TABULATE
FORMAT STUB model
FORMAT hp
  RENAMING * => '{:num %\'d}'
FORMAT msrp
  RENAMING * => '${:num %\'d}'
```

---

## 14. Percent formatting from proportions

**gt**
```{r}
pizzaplace |>
  dplyr::mutate(month = as.numeric(substr(date, 6, 7))) |>
  dplyr::count(month, name = "pizzas_sold") |>
  dplyr::mutate(pct_of_annual = pizzas_sold / sum(pizzas_sold)) |>
  gt(rowname_col = "month") |>
  fmt_integer(columns = pizzas_sold) |>
  fmt_percent(columns = pct_of_annual, decimals = 1)
```

**GTSQL**
```sql
WITH monthly AS (
  SELECT CAST(SUBSTR(date, 6, 2) AS INT) AS month, COUNT(*) AS pizzas_sold
  FROM pizzaplace
  GROUP BY 1
),
totals AS (SELECT SUM(pizzas_sold) AS total FROM monthly)
SELECT m.month, m.pizzas_sold, 1.0 * m.pizzas_sold / t.total AS pct_of_annual
FROM monthly m CROSS JOIN totals t

TABULATE month, pizzas_sold, pct_of_annual
FORMAT STUB month
FORMAT pizzas_sold
  RENAMING * => '{:num %\'d}'
FORMAT pct_of_annual
  RENAMING * => '{:num %.1f}%'
```

---

## 15. Scientific notation

**gt**
```{r}
dplyr::tibble(
  small = 10^(-6:-1),
  large = 10^(1:6)
) |>
  gt() |>
  fmt_scientific()
```

**GTSQL**
```sql
TABULATE small, large FROM powers
FORMAT small, large
  RENAMING * => '{:num %.2e}'
```

---

## 16. Date formatting

**gt**
```{r}
exibble |>
  dplyr::select(date, time) |>
  gt() |>
  fmt_date(columns = date, date_style = "month_day_year")
```

**GTSQL**
```sql
TABULATE date, time FROM exibble
FORMAT date
  RENAMING * => '{:time %B %d, %Y}'
```

---

## 17. Date + time + datetime in one table

**gt**
```{r}
exibble |>
  dplyr::select(date, time, datetime) |>
  dplyr::slice(1:4) |>
  gt() |>
  fmt_date(columns = date, date_style = "day_month_year") |>
  fmt_time(columns = time, time_style = "h_m_p") |>
  fmt_datetime(
    columns = datetime,
    format = "EEEE, MMMM d, y 'at' h:mm a"
  )
```

**GTSQL**
```sql
SELECT date, time, datetime FROM exibble LIMIT 4
TABULATE
FORMAT date
  RENAMING * => '{:time %d %B %Y}'
FORMAT time
  RENAMING * => '{:time %I:%M %p}'
FORMAT datetime
  RENAMING * => '{:time %A, %B %d, %Y at %I:%M %p}'
```

---

## 18. Replace missing values

**gt**
```{r}
exibble |>
  dplyr::select(num, char, currency) |>
  gt() |>
  sub_missing(columns = num,      missing_text = "N/A") |>
  sub_missing(columns = char,     missing_text = "(none)") |>
  sub_missing(columns = currency, missing_text = "---")
```

**GTSQL**
```sql
TABULATE num, char, currency FROM exibble
FORMAT num
  RENAMING null => 'N/A'
FORMAT char
  RENAMING null => '(none)'
FORMAT currency
  RENAMING null => '---'
```

---

## 19. Replace zero values

**gt**
```{r}
dplyr::tibble(
  product  = c("Widget A", "Widget B", "Widget C"),
  in_stock = c(150, 0, 75),
  on_order = c(0, 200, 0)
) |>
  gt() |>
  fmt_integer() |>
  sub_zero(columns = in_stock, zero_text = "Out of stock") |>
  sub_zero(columns = on_order, zero_text = "-")
```

**GTSQL**
```sql
TABULATE product, in_stock, on_order FROM inventory
FORMAT in_stock, on_order
  RENAMING * => '{:num %\'d}'
FORMAT in_stock
  RENAMING 0 => 'Out of stock'
FORMAT on_order
  RENAMING 0 => '-'
```

---

## 20. Direct value mapping (text_case_match)

**gt**
```{r}
dplyr::tibble(
  feature   = c("API", "Dashboard", "Reports", "Settings"),
  available = c("Y", "N", "Y", "P")
) |>
  gt() |>
  text_case_match(
    "Y" ~ "✓ Yes",
    "N" ~ "✗ No",
    "P" ~ "◐ Partial",
    .locations = cells_body(columns = available)
  )
```

**GTSQL**
```sql
TABULATE feature, available FROM features
FORMAT available
  RENAMING 'Y' => '✓ Yes',
           'N' => '✗ No',
           'P' => '◐ Partial'
```

---

## 21. Per-column locale (French dates)

**gt**
```{r}
exibble |>
  dplyr::select(date) |>
  gt() |>
  fmt_datetime(columns = date, format = "EEEE d MMMM y", locale = "fr")
```

**GTSQL**
```sql
TABULATE date FROM exibble
FORMAT date
  SETTING locale => 'fr'
  RENAMING * => '{:time %A %d %B %Y}'
```

---

## 22. Continuous color scale with explicit domain

**gt**
```{r}
sp500 |>
  dplyr::filter(date >= "2015-01-01" & date <= "2015-01-15") |>
  dplyr::select(date, open, high, low, close) |>
  gt() |>
  fmt_currency(columns = c(open, high, low, close), decimals = 2) |>
  data_color(
    columns = c(open, high, low, close),
    palette = "RdYlGn",
    domain  = c(1990, 2090)
  )
```

**GTSQL**
```sql
SELECT date, open, high, low, close
FROM sp500
WHERE date BETWEEN '2015-01-01' AND '2015-01-15'

TABULATE
FORMAT open, high, low, close
  RENAMING * => '${:num %\'.2f}'
SCALE background FROM (1990, 2090) TO RdYlGn
  SETTING target => (open, high, low, close)
```

---

## 23. Color scale with auto-inferred domain

**gt**
```{r}
towny |>
  dplyr::select(name, population_2021) |>
  dplyr::slice_max(population_2021, n = 8) |>
  gt() |>
  fmt_integer(columns = population_2021) |>
  data_color(
    columns = population_2021,
    palette = c("#f7fbff", "#08306b")
  )
```

**GTSQL**
```sql
SELECT name, population_2021
FROM towny
ORDER BY population_2021 DESC
LIMIT 8

TABULATE
FORMAT population_2021
  RENAMING * => '{:num %\'d}'
SCALE background TO ('#f7fbff', '#08306b')
  SETTING target => population_2021
```

---

## 24. Named viridis palette

**gt**
```{r}
gtcars |>
  dplyr::select(mfr, model, hp, mpg_c) |>
  dplyr::slice_head(n = 12) |>
  gt() |>
  data_color(columns = hp, palette = "viridis")
```

**GTSQL**
```sql
SELECT mfr, model, hp, mpg_c FROM gtcars LIMIT 12
TABULATE
SCALE background TO viridis
  SETTING target => hp
```

---

## 25. Log-scaled color mapping

**gt**
```{r}
world_data <- dplyr::tibble(
  country        = c("Luxembourg", "United States", "Germany", "Japan",
                     "China", "Brazil", "India", "Nigeria",
                     "Ethiopia", "Burundi"),
  population     = c(0.65e6, 331e6, 83e6, 125e6,
                     1412e6, 214e6, 1408e6, 213e6,
                     120e6, 12e6),
  gdp_per_capita = c(125000, 76000, 52000, 34000,
                     12700, 9700, 2500, 2100,
                     1000, 250)
)

world_data |>
  gt() |>
  data_color(
    columns = gdp_per_capita,
    fn = function(x) {
      scales::col_numeric(
        palette = c("white", "darkgreen"),
        domain  = log10(c(1, 100000))
      )(log10(pmax(x, 1)))
    }
  )
```

**GTSQL**
```sql
TABULATE country, population, gdp_per_capita FROM world_data
SCALE background FROM (0, 100000) TO ('white', 'darkgreen') VIA log10
  SETTING target => gdp_per_capita
```

---

## 26. Conditional cell highlight (single column)

**gt**
```{r}
students <- dplyr::tibble(
  name  = c("Alice", "Bob", "Carla", "Dan", "Eve", "Frank"),
  score = c(92, 58, 74, 45, 88, 67),
  grade = c("A", "F", "C", "F", "B", "D")
)

students |>
  gt() |>
  tab_style(
    style    = list(cell_text(weight = "bold", color = "red")),
    locations = cells_body(columns = score, rows = score < 60)
  )
```

**GTSQL**
```sql
TABULATE name, score, grade FROM students
HIGHLIGHT score
  FILTER score < 60
  SETTING face => 'bold', color => 'red'
```

---

## 27. Multi-column conditional highlight

**gt**
```{r}
sales <- dplyr::tibble(
  region  = c("North", "South", "East", "West"),
  revenue = c(120000, 98000, 145000, 132000),
  units   = c(1200, 980, 1450, 1320),
  margin  = c(0.18, 0.22, 0.15, 0.27)
)

sales |>
  gt() |>
  tab_style(
    style     = cell_fill(color = "#fff3cd"),
    locations = cells_body(
      columns = c(revenue, units, margin),
      rows    = region == "West"
    )
  )
```

**GTSQL**
```sql
TABULATE region, revenue, units, margin FROM sales
HIGHLIGHT revenue, units, margin
  FILTER region = 'West'
  SETTING background => '#fff3cd'
```

---

## 28. Up/down day stock highlight (two HIGHLIGHTs)

**gt**
```{r}
sp500 |>
  dplyr::filter(date >= "2015-12-01" & date <= "2015-12-15") |>
  dplyr::select(date, open, close) |>
  gt() |>
  fmt_currency(columns = c(open, close)) |>
  tab_style(
    style     = list(cell_fill(color = "#90EE90"), cell_text(weight = "bold")),
    locations = cells_body(rows = close > open)
  ) |>
  tab_style(
    style     = list(cell_fill(color = "#FFB6C1"), cell_text(weight = "bold")),
    locations = cells_body(rows = close < open)
  )
```

**GTSQL**
```sql
SELECT date, open, close
FROM sp500
WHERE date BETWEEN '2015-12-01' AND '2015-12-15'

TABULATE
FORMAT open, close
  RENAMING * => '${:num %\'.2f}'
HIGHLIGHT date, open, close
  FILTER close > open
  SETTING background => '#90EE90', face => 'bold'
HIGHLIGHT date, open, close
  FILTER close < open
  SETTING background => '#FFB6C1', face => 'bold'
```

---

## 29. Summary rows: single sum

**gt**
```{r}
quarterly_sales <- dplyr::tibble(
  category = c("Hardware", "Hardware", "Software", "Software"),
  product  = c("Widget", "Gadget", "Gizmo", "Doohickey"),
  revenue  = c(45000, 62000, 38000, 51000),
  units    = c(450, 620, 380, 510)
)

quarterly_sales |>
  gt(groupname_col = "category") |>
  summary_rows(
    columns = c(revenue, units),
    fns     = list("sum")
  )
```

**GTSQL**
```sql
TABULATE product, revenue, units FROM quarterly_sales
FACET category
  SETTING target => (revenue, units),
          aggregate => ('sum')
```

---

## 30. Summary rows: min/max/mean with labels

**gt**
```{r}
sp500 |>
  dplyr::filter(date >= "2015-01-05" & date <= "2015-01-16") |>
  dplyr::mutate(week = paste("Week of", format(lubridate::floor_date(date, "week"), "%b %d"))) |>
  gt(rowname_col = "date", groupname_col = "week") |>
  summary_rows(
    columns = c(open, high, low, close),
    fns     = list(Min = "min", Max = "max", Avg = "mean"),
    fmt     = ~ fmt_number(., decimals = 2)
  )
```

**GTSQL**
```sql
SELECT date, open, high, low, close,
       'Week of ' || strftime('%b %d', date('start of week')) AS week
FROM sp500
WHERE date BETWEEN '2015-01-05' AND '2015-01-16'

TABULATE date, open, high, low, close
FORMAT STUB date
FORMAT open, high, low, close
  RENAMING * => '{:num %\'.2f}'
FACET week
  SETTING target => (open, high, low, close),
          aggregate => ('min', 'max', 'mean'),
          label => ['Min', 'Max', 'Avg'],
          side => 'bottom'
```

---

## 31. Title-case transformation

**gt**
```{r}
penguins |>
  dplyr::select(species, island, body_mass) |>
  dplyr::slice_head(n = 6) |>
  gt() |>
  text_transform(
    locations = cells_body(columns = c(species, island)),
    fn        = function(x) tools::toTitleCase(tolower(x))
  )
```

**GTSQL**
```sql
SELECT species, island, body_mass FROM penguins LIMIT 6
TABULATE
FORMAT species, island
  RENAMING * => '{:Title}'
```

---

## 32. Forced-sign percent (growth rates)

**gt**
```{r}
growth <- dplyr::tibble(
  region      = c("North", "South", "East", "West", "Central"),
  growth_rate = c(0.045, -0.021, 0.083, -0.067, 0.012)
)

growth |>
  gt() |>
  fmt_percent(columns = growth_rate, decimals = 1, force_sign = TRUE)
```

**GTSQL**
```sql
TABULATE region, growth_rate FROM growth
FORMAT growth_rate
  RENAMING * => '{:num %+.1f}%'
```

---

## 33. Comprehensive: sales report with header, spanner, formatting, scale, highlight, summary

**gt**
```{r}
set.seed(42)
sales_data <- tidyr::expand_grid(
  year    = c(2023, 2024),
  region  = c("North", "South", "East", "West"),
  quarter = c("Q1", "Q2", "Q3", "Q4")
) |>
  dplyr::mutate(
    revenue      = round(runif(dplyr::n(), 50, 200), 1),
    units_sold   = sample(500:2500, dplyr::n(), replace = TRUE),
    satisfaction = round(runif(dplyr::n(), 0.55, 0.95), 2)
  )

quarterly <- sales_data |>
  dplyr::filter(year == 2024) |>
  dplyr::group_by(region, quarter) |>
  dplyr::summarize(
    revenue      = sum(revenue),
    units        = sum(units_sold),
    satisfaction = mean(satisfaction),
    .groups = "drop"
  )

quarterly |>
  gt(rowname_col = "quarter", groupname_col = "region") |>
  tab_header(
    title    = "2024 Sales Performance",
    subtitle = "By Region and Quarter"
  ) |>
  tab_spanner(label = "Financial", columns = c(revenue, units)) |>
  fmt_currency(columns = revenue, decimals = 1) |>
  fmt_integer(columns = units) |>
  fmt_percent(columns = satisfaction, decimals = 1, scale_values = FALSE) |>
  cols_label(
    revenue      = "Revenue",
    units        = "Units Sold",
    satisfaction = "CSAT Score"
  ) |>
  summary_rows(
    columns = c(revenue, units),
    fns     = list(Total = "sum", Average = "mean")
  ) |>
  data_color(
    columns = satisfaction,
    palette = c("white", "green"),
    domain  = c(0, 1)
  ) |>
  tab_style(
    style     = list(cell_text(weight = "bold", color = "red")),
    locations = cells_body(columns = satisfaction, rows = satisfaction < 0.7)
  )
```

**GTSQL**
```sql
WITH quarterly AS (
  SELECT region, quarter,
         SUM(revenue) AS revenue,
         SUM(units_sold) AS units,
         AVG(satisfaction) AS satisfaction
  FROM sales_data
  WHERE year = 2024
  GROUP BY region, quarter
)

TABULATE region, quarter, revenue, units, satisfaction FROM quarterly

FORMAT STUB quarter
FORMAT SPAN revenue, units AS financial

FORMAT revenue
  RENAMING * => '${:num %\'.1f}'
FORMAT units
  RENAMING * => '{:num %\'d}'
FORMAT satisfaction
  RENAMING * => '{:num %.1f}%'

FACET region
  SETTING target => (revenue, units),
          aggregate => ('sum', 'mean'),
          label => ['Total', 'Average'],
          side => 'bottom'

SCALE background FROM (0, 1) TO ('white', 'green')
  SETTING target => satisfaction

HIGHLIGHT satisfaction
  FILTER satisfaction < 0.7
  SETTING face => 'bold', color => 'red'

LABEL
  title => '2024 Sales Performance',
  subtitle => 'By Region and Quarter',
  financial => 'Financial',
  revenue => 'Revenue',
  units => 'Units Sold',
  satisfaction => 'CSAT Score'
```

---

## Notes on omissions

The following table types from the source book are intentionally **not** in the
corpus because GTSQL cannot currently express them:

- Multi-column stubs (`rowname_col = c("region", "category")`).
- `cols_units()` and the `{{ ... }}` units-in-label notation — GTSQL does not currently expose a units setting; embed the unit in the column label string instead.
- Tables with cell footnotes (`tab_footnote()`) or per-element styling of the
  table footer beyond `caption`.
- Tables that re-order rows via `row_order()` / `row_group_order()` after
  creation — equivalent ordering must be done in the upstream `SELECT ... ORDER
  BY`.
- Tables using `tab_spanner_delim()` to derive spanners from delimited column
  names — equivalent must be expressed via explicit `FORMAT SPAN` clauses.
- Stub indentation (`tab_stub_indent()`).
- Nanoplots (`cols_nanoplot()`).
- `grand_summary_rows()` (table-wide totals; the closest GTSQL equivalent is a `FACET` clause with no grouping column, but this maps to `summary_rows()` semantics rather than a true grand summary).
- `text_transform()` with arbitrary R functions; only literal value-to-string
  mapping is supported via `RENAMING <value> => '<string>'`.
- `from_column()` dynamic parameters (e.g. per-row currency code or decimal
  precision pulled from another column).
- Global theming via `tab_options()` / `opt_*()` helpers.
